% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments

At first, I must thank Prof Zhang for introducing me the interesting world of computer animation research.
Prof Zhang is a great supervisor, who gives the students freedom to pursue their own research interest. 
 
I'm very grateful to Dr Xiaosong Yang, my second supervisor.
Besides the knowledge and advice, it must have cost your and Dr Ren lots of effort to take care of every trouble during my study in UK.
 
I would also never forget my best friend at NCCA, Richard Southern; your critical questions greatly reshaped my thoughts.
Without your help, so much research work may lie unproven or unnoticed.
Even someone may still find the thesis still hard to understand, it is all my fault.
My original draft is awful, by asking me hundreds of embarrassing questions, Richard has taught me how should I present my work.
Richard Southern is the first and maybe the only one who fully understand my work at current.
 And your encouragement is crucial during the time of misunderstood, disappointment and loneliness.

Also I must express my gratitude to  Lady Jie Zhang. 
Your support is the most valuable thing during my hardiest time.

Dr You and Ms Sue Court have taken great effort in refine the English of the thesis.


Also many thanks go to Jon Macey, Phil Spicer, Ian Stephenson and  Ari Sarafopoulos for the wonderful lectures.

Thanks goes to Peter Comninos  for providing the casual job opportunity to finance the last days of my PhD.

I must also thank many researcher such as Dr Jianchang, Dr Hongchuan Yu Dr Hammadi Nait-Charif, Dr Zhidong Xiao, Dr Oleg Fryazinov for the discussion during the reading group.






Also many PhD students provide every kinds of help in the research work and my study.
I would thank Denis Kravtsov for his insights into Graphics and Programming, after your leave, coding at lab becomes a more and more  boring task. 
Dr Olusola Aina is encouraging and very helpful for the latex.
Dan Shepherd have given  very valuable advice when I started my PhD study.
Shihui Guo, Huiwen Zhao, Meili Wang, Wenxi Li and Min Jiang, Xinzhen, Dr Jiao , Dr Pan and many others PhDs candidates and masters for  bringing fun into my busy study life.


I would also thank Craig Senior for maintain my computer and software over these years.
Jan Lewis , Dan Cox for the administrating work.
And many more people at NCCA and Bournemouth University that I can not name who help me understand CG and Film in UK.

I’m also thankful to the China Scholar Council for their financial funding and Mr Quanshen Chang and Ms Li Zhu for the administration.
 
 
 
 
 
 
 


\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
